R Notebook for conducting Minimum Detectable Change (MDC) Analysis to design a monitoring strategy for the Upper Yaquina River TMDL Implementation Plan

### 2024-02-21 msc.Rmd
I think I need to incorperate the varriation in the sampling time step among the samples

  # Calculate the MDC using the SE_b from the model
  # Note: This calculation assumes SE_b remains constant with additional samples, which might not be accurate
  MDC <- (t_alpha + t_beta) * SE_b

@@

print(paste("MDC for", initial_n + additional_samples, "total samples:", 
            sprintf("%.2f", abs(10^(MDC_add) - 1) * 100)), "% compared to",
            sprintf("%.2f", abs((1 - 10^(-MDC_cur)) * 100)),
            "% for", initial_n, "initial samples"))

@@

>>>>

  # Calculate the MDC using the SE_b from the model
  # Note: This calculation assumes SE_b remains constant with additional samples, which might not be accurate
  MDC <- (t_alpha + t_beta) * SE_b * 365

@@

print(paste("MDC for", initial_n + additional_samples, "total samples:", 
            sprintf("%.2f", abs(10^(MDC_add) - 1) * 100), "% compared to",
            sprintf("%.2f", abs(10^(MDC_cur) - 1) * 100),
            "% for", initial_n, "initial samples"))

@@

I need a way to incorporate the x data into the regression statistics and MDC. I think the approach as is assumes that each additional sample is collected at a constant step in x (or time in my case).
